% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
\usepackage[pdftex,
            pdfauthor={Gerard Casas Saez},
            pdftitle={Gerard's resume},
            pdfsubject={Gerard Casas Saez personal resume and CV},
            pdfkeywords={resume, cv, Gerard Casas, software engineer,},
            pdfproducer={Latex with hyperref},
            pdfcreator={pdflatex, or other tool}]{hyperref}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
 \textbf{\large Gerard Casas Saez}& \href{mailto:contact@gerard.space}{contact@gerard.space} \\
  \textbf{Website:} \href{https://gerard.space}{gerard.space} \textbf{GitHub:} \href{https://github.com/casassg}{@casassg} & 
  +17207551095
\end{tabular*}
\\

\vspace{0.1in}
\resheading{Summary}
	\begin{itemize}
		\resitem{Interested in building Machine Learning and Data products and infrastructure at scale.}
		\resitem{Work experience in Machine Learning infrastructure particularly on automatic retraining pipelines.  }
		\resitem{Research experience on live data collection systems for data analysis.}
		\resitem{Contributed to several open-Source projects like Apache Airflow, Kubeflow Pipelines and Tensorflow Extended.}
		
	\end{itemize}
% \resheading{Research experience}
% 	\begin{itemize}
% 		\item
% 			\ressubheading{Project EPIC, Colorado University}{Boulder, CO}{Research intern}{Research intern, February 2017 - present}
% 			\begin{itemize}
% 				\item Developed infrastructure to collect and analyze Twitter data in real time with an average of 2000 tweets/minute
% 				\item Written \textit{Big Data Analytics in Container Orchestrated Systems} as my B.S. thesis.
% 				\item Designed and built big data analytics system prototype on Kubernetes.
% 			\end{itemize}
% 	\end{itemize}

\resheading{Experience}
	\begin{itemize}
		\item
			\ressubheading{Twitter}{Boulder, CO}{Senior Machine Learning Engineer}{Senior Machine Learning Engineer, April 2022 - Present}
			\begin{itemize}
				\resitem{Technical lead for the ML Pipelines team on Cortex Platform.} 

				\resitem{Led KFP SDK internal general adoption across the company.}
				\resitem{Worked on pipelines python client authentication and  next-gen component authoring.}
				\resitem{Built internal command line tool for KFP Pipelines continuous release.}
				\resitem{Worked as point of contact for industry collaborations with Spotify and Google.}
				\resitem{Mentored team members helping scope and drive projects for the ML Pipelines team.}
				\resitem{Defined quarterly roadmap, drove project alignment across teams, improved team execution with Kanban.}
				
			\end{itemize}
		\item
			\ressubheading{Twitter}{Boulder, CO}{Machine Learning Engineer II}{Machine Learning Engineer II, October 2020 - April 2022}
			\begin{itemize}
				\resitem{Led development for team CI/CD system improving code and documentation stability. } 

				\resitem{Developed initial python wheel and VSCode Twitter monorepo integrations used by 100s of engineers.}
				\resitem{Co-led/designed TFX pipeline production scheduling for Kubeflow Pipeline clusters.}
				\resitem{Led pipeline integration for GPU training using AI Platform Training.}
				\resitem{Co-authored evaluation for next-gen ML Training Service on GCP.}
				\resitem{Taught "ML at Scale on GCP with TFX" class for internal Hackweek with over 300 virtual attendees.}
				\resitem{Collaborated with customer teams to launch the first ads click model migration to GCP with improved developer iteration, leading to faster model improvements.}
			    \resitem{Cross-team mentoring to build new pipeline components that integrate well across platform.}
				\resitem{Member of various working groups like ML to GCP virtual team, and Python Customer Advisory Board.}
				\resitem{Multiple contributions to TFX, and Kubeflow Pipelines OSS projects.}

				
			\end{itemize}
		\item
			\ressubheading{Twitter}{Boulder, CO}{Machine Learning Engineer}{Machine Learning Engineer, September 2019 - October 2020}
			\begin{itemize}
				\resitem{Contributed to internal distributed Bayesian hyperparameter optimization framework based on \href{https://ax.dev}{Ax.dev}.} 
				\resitem{Supported ML research work for "Tuning Word2vec for Large Scale Recommendation Systems" (\href{https://arxiv.org/pdf/2009.12192.pdf}{RecSys2020}).}
				\resitem{Worked on evaluation of industry pipeline solutions and eventual adoption of TFX for defining end-to-end ML pipelines.}
			\end{itemize}
		\item
			\ressubheading{Project EPIC, University of Colorado Boulder}{Boulder, CO}{Research Assistant}{Research Assistant, February 2017 - August 2019}
			\begin{itemize}
				\resitem{Analyzed 2000 tweets/minute of real time data by building Big Data pipeline using Spark, Kafka and Cassandra.} 
				\resitem{Deployed system prototype with Kubernetes using custom microservices written in Go and Python.}
			\end{itemize}
			\item
			\ressubheading{Twitter}{Boulder, CO}{Software Engineering intern}{Software Engineering intern, May 2018 - August 2018}
			\begin{itemize}
				\resitem{Developed CLI to deploy Apache Airflow instances internally.}
				\resitem{Helped reduce ML model training and deploy time by 1/4 developing \href{https://blog.twitter.com/engineering/en_us/topics/insights/2018/ml-workflows.html}{ML Workflows}.}
			\end{itemize}
		\item
			\ressubheading{inLab FIB}{Barcelona, Spain}{Web Development Intern}{Web Development Intern, March 2015 - January 2017}
			\begin{itemize}
				\resitem{Built REST API for faculty data - Average usage of 25.000 daily accesses. (Django, Python)}
				\resitem{Reduced Oracle SQL query response time by 1/3 using non-blocking updates and materialized views.}
			\end{itemize}

		\item
			\ressubheading{con terra GmbH}{Münster, Germany}{Intern}{Intern, Summer 2015}
			\begin{itemize}
				% \resitem{Analyzed travel distances Bundesliga fans by team (FME Desktop - ETL tool)}
				\resitem{Developed bike share routing app using OpenStreetMap open data and Citibikes API. (Javascript)}
			\end{itemize}
		% \item
		% 	\ressubheading{YMCA of Greater Indianapolis}{St. Paul, IN}{Summer camp counselor}{Summer camp counselor, Summer 2013 \& 2014 \& 2016}
		% 	\begin{itemize}
		% 		\resitem{Supervised groups of approximately 12 campers in resident camp setting.}
		% 	\end{itemize}
	\end{itemize}
\break
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheadinged{University of Colorado Boulder}{Boulder, CO}{M.S., Computer Science (GPA 3.97)}{August 2017 - August 2019}
			\begin{itemize}
				\resitem{\textbf{Courses:} Analysis and Design of Algorithms, User Centered Design, Database Systems, Big Data Architecture, Machine Learning, Computational Genomics, Natural Language Processing.}
			\end{itemize}

		\item
			\ressubheadinged{Universitat Polit\`ecnica de Catalunya}{Barcelona, Spain}{B.S., Computer Science (8.8/10)}{September 2013 - July 2017}
			\begin{itemize}
				\resitem{\textbf{Courses:} Data Mining, Data Compression, Programming Languages, Software architecture, Databases, Parallelism, Project Management, Web architecture, Android, NoSQL databases, Reflective programming.}
			\end{itemize}

	\end{itemize}

\resheading{Open Source projects}
	\begin{itemize}
% 		\item
% 			\ressubheading{gTweetMap, a tool for the Geolocation of social Movements}{Barcelona, Spain}{Student}{Spring 2013}
% 			\begin{itemize}
% 				\resitem{Built geolocated tweets tracker app to study social movements.}
% 			\end{itemize}
\item 
		\ressubheading{TFX Addons SIG}{Boulder, CO}{Core Contributor}{Core Contributor, May 2021 - Present}
			\begin{itemize}
				\resitem{Release manager from version 0.1.0 to date.}
				\resitem{Mentored new contributors developing new components with reliable tests, and consistent codebase practices.}
				\resitem{Contributor and maintainer for project CI/CD system, XGBoostEvaluator, FeastExampleGen and others.}
				\resitem{Collaborator for ModelCardToolking migration mentoring Twitter team members to contribute to project.} 
			\end{itemize}
		\item
			\ressubheading{
AIP-31: Airflow functional DAG definition / "Taskflow API"}{Boulder, CO, USA}{ML Engineer}{Core Contributor, January 2020 - July 2020}
			\begin{itemize}
				\resitem{Proposed and implemented improvement for Airflow DAG user experience adding explicit XCom data.}
				\resitem{Released in Airflow 2.0.0 and used in one of the main tutorials for the project.}
				
			\end{itemize}
			
	\end{itemize}

% \resheading{Leadership}
	
% 	\begin{itemize}
% 	    \item 
% 		\ressubheading{TFX Addons SIG, OSS}{Boulder, CO}{Core Contributor}{Core Contributor/Release manager, May 2021 - Present}
% 			\begin{itemize}
% 				\resitem{Release manager from version 0.1.0 to date.}
% 				\resitem{Mentored new contributors developing new components with reliable tests, and consistent codebase practices.}
% 				\resitem{Contributor and maintainer for project CI/CD system, XGBoostEvaluator, FeastExampleGen and others.}
% 				\resitem{Collaborator for ModelCardToolking migration mentoring internal members to contribute to project} 
% 			\end{itemize}
% 		\item 
% 			\ressubheading{HackCU, University of Colorado Boulder}{Boulder, CO}{Tech director}{Tech director, February 2017 - April 2019}
% 			\begin{itemize}
% 				\resitem{Co-directed Colorado's biggest student hackathon with 600 attendees and a 15 people core team.}
% 			\end{itemize}
% 		\item
% 			\ressubheading{HackUPC, Universitat Polit\`ecnica de Catalunya}{Barcelona, Spain}{Co-Director and organizer}{Co-Director, November 2015 - September 2018}
% 			\begin{itemize}
% 				\resitem{Co-directed Spain's biggest student hackathon with 500 attendees and a 20 people core team.}
% 				% \item Directed web development team with 5 person team for 2 editions.
% 			\end{itemize}
% 	\end{itemize}

\resheading{Awards}
	\begin{itemize}
		\resitem{\href{https://opensource.googleblog.com/2022/03/Announcing-First-Group-of-Google-Open-Source-Peer-Bonus-Winners-in-2022.html}{\textbf{Google OSS Peer Bonus for contributions to TFX and TFX Addons} (2022)}}
		\resitem{\textbf{Denver Government award winner at ETHDenver.} (2018)}
		\resitem{\textbf{Grant winner at MD5 Physical Cyber Hackathon.} (2018)}
		\resitem{\textbf{Balsells Fellowship.} (2017-2019, two years of funding for graduate studies)}
		\resitem{\textbf{Balsells Mobility program.} (2017, five months of funding for research)}
		% \resitem{Finalist project at OxfordHack 2016. (2016)}
% 		\resitem{\textbf{Nine distinction awards during B.S.} (2013-2017, awarded to 5\% top students per class)}
		% \resitem{\textbf{52North Innovation Incentive Award:} Awarded for gTweetMap, my high school final research project. (2013)}
	\end{itemize}

\resheading{Publications}
	\begin{itemize}
		\item 	Jennings A., Gerard C., Kenneth M. A., Leysia P., and Rebecca M.  \textbf{Incorporating Context and Location Into Social Media Analysis: A Scalable, Cloud-Based Approach for More Powerful Data Science.}  \textit{HICSS 52 (accepted).}
        \item Gerard C. \textbf{Social Media Analysis for Crisis Informatics in the Cloud} \textit{MS Thesis}
	\end{itemize}


\resheading{Skills}
	\begin{itemize}
		\resitem{\textbf{Programming:} Java, Python \textbf{Experience with:} Kubeflow Pipelines, Tensorflow Extended, Django/Flask/FastAPI, SQL, Scala, Tensorflow, Apache Airflow, Apache Beam/Dataflow, HTML, CSS, Haskell, Smalltalk, Go, Spark, Kafka, Kubernetes}
		\resitem{\textbf{Native:} Catalan, Spanish. \textbf{Advanced:} English.}
		\resitem{\textbf{Hobbies:} Skiing, Running, Photography, Roller hockey, Piano, Swim.}
% 		\resitem{\textbf{Hackathon participation:} OxfordHack, BrumHack 4.0, MHacks 9, HackJunction, T9Hacks, ETHDenver.}
	\end{itemize}



\end{document}
